Equalizer\\Programming and User Guide

### 2011-05-26 Developer/ProgrammingGuide/paper.tex
Minor spelling fix in programming guide
Small wording fix
[ ] May break build
[ ] May break existing applications (see CHANGES.txt)
[x] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[ ] Documentation

When using \textsf{commit} on slave object instances, multiple modifications on
the same database may happen simultaneously. To avoid excessive synchronization
in the network layer, Equalizer a lightweight approach which requires the
application to avoid or handle conflicting changes on the same object.

@@

The barrier uses both the data distribution for synchronizing its data,
as well as custom command packets to implement the barrier logics. A
barrier is a versioned object. Each version can have a different height,
and enter request are automatically grouped together by version.

@@

The Equalizer entities use the common base class
\textsf{eq::fabric::Object}. This class manages common entity data, and is not
intended to by subclassed directly.  The inheritance chain \textsf{eq::View}
$\rightarrow$ \textsf{eq::fabric::View} $\rightarrow$
\textsf{eq::fabric::Object} $\rightarrow$ \textsf{eq::fabric::Se\-rial\-izable}
$\rightarrow$ \textsf{co::Object} serves as sample implementation for this
process.

>>>>

When using \textsf{commit} on slave object instances, multiple modifications on
the same database may happen simultaneously. To avoid excessive synchronization
in the network layer, Equalizer implements a lightweight approach which requires the
application to avoid or handle conflicting changes on the same object.

@@

The barrier uses both the data distribution for synchronizing its data,
as well as custom command packets to implement the barrier logics. A
barrier is a versioned object. Each version can have a different height,
and enter requests are automatically grouped together by version.

@@

The Equalizer entities use the common base class
\textsf{eq::fabric::Object}. This class manages common entity data, and is not
intended to be subclassed directly.  The inheritance chain \textsf{eq::View}
$\rightarrow$ \textsf{eq::fabric::View} $\rightarrow$
\textsf{eq::fabric::Object} $\rightarrow$ \textsf{eq::fabric::Se\-rial\-izable}
$\rightarrow$ \textsf{co::Object} serves as sample implementation for this
process.
